Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
Footnote placement

The RO-Crate community is strongly engaged with the European-wide
biology/bioinformatics collaborative e-Infrastructure, ELIXIR
\cite{doi:10.1016/j.tibtech.2012.02.002}, along with European Open Science
Cloud (EOSC\footnote{\url{https://eosc.eu/}}) projects including
EOSC-Life,\footnote{\url{https://www.eosc-life.eu/}}
FAIRplus,\footnote{\url{https://fairplus-project.eu/}}
CS3MESH4EOSC\footnote{\url{https://cs3mesh4eosc.eu/}} and
BY-COVID.\footnote{\url{https://by-covid.eu/}} RO-Crate has also established
collaborations with Bioschemas \cite{bioschemas_2017}, GA4GH
\cite{doi:10.1016/j.xgen.2021.100029}, OpenAIRE \cite{rettberg_2015_openaire}
and multiple H2020 projects.

@@

Further work during 2019 started adapting the DataCrate documentation
through a more collaborative and exploratory \textit{RO Lite} phase, initially
using Google Docs for review and discussion, then moving to GitHub as a
collaboration space for developing what is now the RO-Crate
specification, maintained as
Markdown\footnote{\url{https://github.com/researchobject/ro-crate/}} in GitHub Pages
and published through Zenodo.

@@

The work of the community has led to the development of a number of
tools for creating and using RO-Crates. Table~\ref{tab1} shows the current set
of implementations. Reviewing this list, one can see that tools support
commonly used programming languages, including Python, JavaScript, and
Ruby. Additionally, these tools can be integrated into commonly used
research environments, in particular, the command line tool
\textit{ro-crate-html-js} \cite{ro-crate-html-js} for creating a human-readable
preview of an RO-Crate as a sidecar HTML file. Furthermore, there are
tools that cater to end-users (\textit{Describo} \cite{describo}, \textit{WorkflowHub}
\cite{about-workflowhub}), in order to simplify creating and managing
RO-Crate. For example, Describo was developed to help researchers of
the Australian Criminal Characters
project\footnote{\url{https://criminalcharacters.com/}} annotate historical prisoner
records to gain greater insight into the history of Australia
\cite{doi:10.1080/14490854.2020.1796500}.

>>>>

The RO-Crate community is strongly engaged with the European-wide
biology/bioinformatics collaborative e-Infrastructure ELIXIR
\cite{doi:10.1016/j.tibtech.2012.02.002}, along with European Open Science
Cloud\footnote{\url{https://eosc.eu/}} (EOSC) projects including
EOSC-Life,\footnote{\url{https://www.eosc-life.eu/}}
FAIRplus,\footnote{\url{https://fairplus-project.eu/}}
CS3MESH4EOSC\footnote{\url{https://cs3mesh4eosc.eu/}} and
BY-COVID.\footnote{\url{https://by-covid.eu/}} RO-Crate has also established
collaborations with Bioschemas \cite{bioschemas_2017}, GA4GH
\cite{doi:10.1016/j.xgen.2021.100029}, OpenAIRE \cite{rettberg_2015_openaire}
and multiple H2020 projects.

@@

Further work during 2019 started adapting the DataCrate documentation
through a more collaborative and exploratory \textit{RO Lite} phase, initially
using Google Docs for review and discussion, then moving to GitHub as a
collaboration space for developing what is now the RO-Crate
specification, maintained\footnote{\url{https://github.com/researchobject/ro-crate/}} as
Markdown in GitHub Pages
and published through Zenodo.

@@

The work of the community has led to the development of a number of
tools for creating and using RO-Crates. Table~\ref{tab1} shows the current set
of implementations. Reviewing this list, one can see support for
commonly used programming languages, including Python, JavaScript, and
Ruby. Additionally, the tools can be integrated into commonly used
research environments, in particular, the command line tool
\textit{ro-crate-html-js} \cite{ro-crate-html-js} for creating a human-readable
preview of an RO-Crate as a sidecar HTML file. Furthermore, there are
tools that cater to end-users (\textit{Describo} \cite{describo}, \textit{WorkflowHub}
\cite{about-workflowhub}), in order to simplify creating and managing
RO-Crate. For example, Describo was developed to help researchers of
the Australian Criminal Characters
project\footnote{\url{https://criminalcharacters.com/}} to annotate historical prisoner
records for greater insight into the history of Australia
\cite{doi:10.1080/14490854.2020.1796500}.
